### 2023-04-10 main/chapter_theory.tex
finish up neutrino majorana etc

>>>>

\subsubsection{Future Majorana-Dirac possibilities}
Future experimental results might resolve the nature of neutrinos.
% 0vBB
If neutrinos have a Majorana nature, then nuclear isotopes that naturally
undergo double-beta decay (emitting two electrons and two neutrinos)
could rarely perform neutrinoless double-beta decay ($0\nu\beta\beta$).
In $0\nu\beta\beta$ events, the two neutrinos annihilate to leave the electrons
emitted back-to-back without missing momentum.
Current results have not observed $0\nu\beta\beta$ decays, but have set limits
on $0\nu\beta\beta$ lifetimes in excess of $10^{21}\,\mathrm{years}$
for many nuclear isotopes~\cite{Bilenky:2014uka}.
Future experiments, such as SuperNEMO~\cite{Barabash:2011row},
will study $0\nu\beta\beta$ with increased precision.

% accelerator experiments
Large upcoming neutrino experiments,
DUNE~\cite{DUNE:2016hlj} and
Hyper-Kamiokande~\cite{Hyper-Kamiokande:2018ofw},
will use accelerator-produced neutrinos to make precise measurements of the
neutrinos' Dirac CP violation,
their mass ordering, and their flavour oscillations.
Although these experiments do not directly probe the neutrinos' possible
Majorana components, they will be indirectly sensitive via the possibility
of exotic new physical effects~\cite{Carrasco-Martinez:2020mlg}.

% reactors
Modern experiments that detect neutrinos from nuclear reactors,
such as JUNO~\cite{JUNO:2015sjr},
are also not directly sensitive to the question of the neutrinos' Majorana
nature.
Along with accelerator experiments, their precise measurements of oscillation
behaviours will, however, help the $0\nu\beta\beta$ studies to more precisely
interpret their data~\cite{Cao:2017drk}.

% etc
Other approaches to testing neutrinos' Majorana nature include studies of
proton-proton collisions~\cite{CMS:2018jxx} or
rare $B$-hadron decays~\cite{LHCb:2014osd,Shuve:2016muy}.
However, these methods are not competitive with the next generation of
$0\nu\beta\beta$ experiments and currently show no Majorana
signal~\cite{Carrasco-Martinez:2020mlg}.
